Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Word Processors

### 2018-08-01 main.tex
Clean version, ready to publish with anonymous authors

\usepackage{styles/thesistitle}

@@

\addbibresource{./bibliography/Bibliography.bib} 
\hypersetup{
	pdftitle	= {Semantic Preserving Bijective Mappings for Representations of Special Functions in Computer Algebra Systems and Word Processors - Exemplified using the DLMF/DRMF, the Word Processor \LaTeX and the Computer Algebra Systems Maple and Mathematica},
	pdfsubject={Master's Thesis in Mathematics, Technische Universität Berlin, July 2017.},
	pdfauthor	= {Andr\'e Greiner-Petter},
	pdfcreator	= {Andr\'e Greiner-Petter},
	pdfkeywords	= {Special Functions, \LaTeX, Translation},
}

@@

%

\title{
    Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Word Processors
}
\author{Andr\'e Greiner-Petter\textsuperscript{1}}
\author{Moritz Schubotz\textsuperscript{1}}
\author{Howard S.~Cohl\textsuperscript{2}}
\author{Bela Gipp\textsuperscript{1}}

\affil{
	\textsuperscript{1}Information Science Group, University of Konstanz, Germany\\
	\url{{first.last}@uni-konstanz.de}
}

\affil{
	\textsuperscript{2}Applied and Computational Mathematics Division,\\
	National Institute of Standards and Technology, Mission Viejo, CA, USA,\\
	\url{howard.cohl@nist.gov}
}

@@

\noindent
{\it \bf Keywords:} \LaTeX, Computer Algebra System (CAS), Translation, Presentation to Computation (P2C)

@@

\begin{wrapfigure}[4]{r}{0.38\textwidth}
\vspace{-10pt}
\begin{minipage}{0.38\textwidth}
\center
\begin{tabular}{lc}
	\hline
	Notation & Expression \\
	\hline
	Infix & $(a+b) \cdot x$\\
	Prefix & $\cdot + a\ b\ x$\\
	Postfix & $a\ b + x\ \cdot$\\
	Functional & $\cdot(+(a, b), x)$\\
	\hline
\end{tabular}
\vspace{-5pt}
\caption{The mathematical expression `$(a+b) \cdot x$' in infix, prefix, postfix and functional notation.}
\label{tab:notations}
\end{minipage}
\vspace{-5pt}
\end{wrapfigure}

@@

\begin{wrapfigure}{r}{0.61\textwidth}
	\vspace{-22pt}
	\centering
	\includegraphics[clip, trim=0.5cm 0.5cm 0.5cm 0.5cm, scale=0.5]{DAGreal.pdf}
	\vspace{-5pt}
	\caption{The internal \Maple{} DAG representation of $x^2+x$.}
	\label{fig:internal-maple-dag}
	\vspace{-15pt}
\end{wrapfigure}

@@

One can access the internal data structure of expressions via the \texttt{ToInert} command, which returns the \inertF. The \inertF{} format is a nested list\footnote{The nested list is a tree representation of a \gls*{dag} that splits nodes with multiple parents into multiple nodes so that each node has only one parent node.} of the internal \gls*{dag} for the given expression. Some of the important types for the nodes are specified in \Cref{tab:maple-types}.
\begin{table}[h]
\centering
\begin{tabular}{cp{10cm}}
	\hline
	Type & Explanation\\
	\hline
	SUM & Sums. Internally stored with factors for each summand, i.e., `$x+y$' would be stored as `$x \cdot 1 + y \cdot 1$'.\\
	PROD & Products.\\
	EXPSEQ & Expression sequence is a kind of list. The arguments of functions are stored in such sequences.\\
	INTPOS & Positive integers.\\
	INTNEG & Negative integers.\\
	COMPLEX & Complex numbers with real and imaginary part.\\
	FLOAT & Float numbers are stored in the scientific notation with integer values for the exponent $n$ and the significand $m$ in $m \cdot 10^n$.\\
	RATIONAL & Rational numbers are fractions stored in integer values for the numerator and positive integers for the denominator.\\
	POWER & Exponentiation with expressions as base and exponent.\\
	FUNCTION & Function invocation with the name, arguments and attributes of the function.\\
	\hline
\end{tabular}
\caption{A subset of important internal \Maple{} data types. See~\parencite{MAPLE:ProgrammingGuide} for a complete list.}
\label{tab:maple-types}
\end{table}
The translator uses the \texttt{OpenMaple}~\parencite[\S 14.3]{MAPLE:ProgrammingGuide} \gls*{api} for interacting with \Maple's kernel implementation.

>>>>

@@

\addbibresource{./bibliography/Bibliography.bib} 
\hypersetup{
	pdftitle	= {Semantic Preserving Bijective Mappings for Representations of Special Functions in Computer Algebra Systems and Word Processors}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%% INFORMATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\title{
    Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Word Processors
}

%\input{authors.tex} %TODO anonymous authors for double blinded review
\author{Anonymous Authors}

@@

\noindent
{\it \bf Keywords:} \LaTeX, Computer Algebra System (CAS), Translation, Presentation to Computation (P2C), Special Functions

@@

\begin{wrapfigure}[10]{r}{0.38\textwidth} % optional parameter gives "# of narrow lines", very useful! 
\vspace{-8pt}
\begin{minipage}{0.38\textwidth}
\center
\begin{tabular}{lc}
	\hline
	Notation & Expression \\
	\hline
	Infix & $(a+b) \cdot x$\\
	Prefix & $\cdot + a\ b\ x$\\
	Postfix & $a\ b + x\ \cdot$\\
	Functional & $\cdot(+(a, b), x)$\\
	\hline
\end{tabular}
%\vspace{-5pt}
\caption{The mathematical expression `$(a+b) \cdot x$' in infix, prefix, postfix and functional notation.}
\label{tab:notations}
\end{minipage}
%\vspace{-5pt}
\end{wrapfigure}

@@

\begin{wrapfigure}[7]{r}{0.61\textwidth}
	\vspace{-15pt}
	\centering
	\includegraphics[clip, trim=0.5cm 0.5cm 0.5cm 0.5cm, scale=0.5]{DAGreal.pdf}
	\vspace{-5pt}
	\caption{The internal \Maple{} DAG representation of $x^2+x$.}
	\label{fig:internal-maple-dag}
	%\vspace{-15pt}
\end{wrapfigure}

@@

One can access the internal data structure of expressions via the \texttt{ToInert} command, which returns the \inertF. The \inertF{} format is a nested list\footnote{The nested list is a tree representation of a \gls*{dag} that splits nodes with multiple parents into multiple nodes so that each node has only one parent node.} of the internal \gls*{dag} for the given expression. Some of the important types for the nodes are specified in \Cref{tab:maple-types}.
\begin{table}[ht]
\centering
\begin{tabular}{cp{10cm}}
	\hline
	Type & Explanation\\
	\hline
	SUM & Sums. Internally stored with factors for each summand, i.e., `$x+y$' would be stored as `$x \cdot 1 + y \cdot 1$'.\\
	PROD & Products.\\
	EXPSEQ & Expression sequence is a kind of list. The arguments of functions are stored in such sequences.\\
	INTPOS & Positive integers.\\
	INTNEG & Negative integers.\\
	COMPLEX & Complex numbers with real and imaginary part.\\
	FLOAT & Float numbers are stored in the scientific notation with integer values for the exponent $n$ and the significand $m$ in $m \cdot 10^n$.\\
	RATIONAL & Rational numbers are fractions stored in integer values for the numerator and positive integers for the denominator.\\
	POWER & Exponentiation with expressions as base and exponent.\\
	FUNCTION & Function invocation with the name, arguments and attributes of the function.\\
	\hline
\end{tabular}
\caption{A subset of important internal \Maple{} data types. See~\parencite{MAPLE:ProgrammingGuide} for a complete list.}
\label{tab:maple-types}
\end{table}
The translator uses the \texttt{OpenMaple}~\parencite[\S 14.3]{MAPLE:ProgrammingGuide} \gls*{api} for interacting with \Maple's kernel implementation.
